Empirical Evaluation of eval in R

### 2020-08-28 inst/analysis/analysis_stable.Rmd

```{r subsample_for_ast}
#ast_sizes <- eval_calls %>% slice_sample(n=10000) %>% mutate(expr_resolved_nodes = map_int(expr_resolved, expr_size_str))
# Now precomputed during the tracing
ast_sizes <- read_fst(path(RUN_DIR, "package-evals-traced.3/summarized-ast-size.fst")) %>% as_tibble() %>% 
      filter(eval_source_type != "<undefined>") %>%
      rename(dataset = eval_source_type) 
```

@@

ast_sizes %>%
  ggplot(aes(x = dataset, y = expr_resolved_nodes, fill = dataset, weight = nb_ev_calls), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=.5)+
  geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
     legend.position=c(0.2, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

@@

Another interesting figure is the degree of consistency of the `expr` argument: how many different types (for `expr_resolved`) are there for one call sites?

r("nb monomorphic", nb_monomorphic)
r("percent monomorphic", ratio(nb_monomorphic, nb_call_sites))

nb
```

>>>>

```{r subsample_for_ast}
#ast_sizes <- eval_calls %>% slice_sample(n=10000) %>% mutate(expr_resolved_nodes = map_int(expr_resolved, expr_size_str))
# Now precomputed during the tracing
ast_sizes <- read_fst(path(RUN_DIR, "package-evals-traced.3/summarized-ast-size.fst")) %>% as_tibble() %>% 
      filter(eval_source_type != "<undefined>")
```

@@

ast_sizes %>%
  ggplot(aes(x = eval_source_type, y = expr_resolved_nodes, fill = eval_source_type, weight = nb_ev_calls)) +
  geom_violin(trim = FALSE, width=.5)+
  #geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

Another interesting figure is the degreee of polymorphism of the `expr` argument: how many different types (for `expr_resolved`) are there for one call sites?

r("nb monomorphic", nb_monomorphic)
r("percent monomorphic", ratio(nb_monomorphic, nb_call_sites))
```

@@
